Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd

# Predator avoidance
Predator avoidance could also contribute to swimming behaviour of caribou
(Miller 2002) <!-- find doi for this article -->. During calving, female caribou
are known to swim to small islands in freshwater lakes give birth, or with their
calves after birth, to avoid predation [@Bergerud_1987]. The use of shoreline
habitat in summer is considered an effective anti-predator calving strategy by
allowing for swimming to islands or peninsulas as a predation avoidance flight
response [@Bergerud_1990]. The use of water, and by association occasionally
swimming, is therefore part of the fine-scale interactions between caribou and
their predators and the use of islands appears to be an effective anti-predator
strategy.

>>>>

# Predator avoidance
Predator avoidance could also contribute to swimming behaviour of caribou
(Miller 2002).<!-- find doi for this article --> During calving, female caribou
are known to swim to small islands in freshwater lakes and give birth, or with their
calves after birth, to avoid predation [@Bergerud_1987]. The use of shoreline
habitat in summer is considered an effective anti-predator calving strategy by
allowing for swimming to islands or peninsulas as a predation avoidance flight
response [@Bergerud_1990]. The use of water, and by association occasionally
swimming, is therefore part of the fine-scale interactions between caribou and
their predators and the use of islands appears to be an effective anti-predator
strategy.
